Peaks Over Threshold for Bursty Time Series

### 2018-05-09 article_springer/article_springer.Rmd
fix cross-refs

#### _Proof of Theorem:_
We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
and then utilize a result by @MeerschaertStoev08. 
The running maximum process is defined as 
$$
M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
$$
and since we assume that the $J_k$ have a continuous distribution, there exist 
norming functions $a(c)$ and $d(c)$ such that 
$$
\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
\longrightarrow F(\ell^*), \quad t \to \infty
$$
where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
value from the support of $F$. 
The CTRM process is then defined via 
$$
V(t) = M(N(t)), \quad t \ge 0
$$
where $N(t)$ is the renewal process associated with the waiting times 
$W_k$: 
$$
N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
$$
Now a key observation is that
$$
T(\ell) = \inf\{t: V(t) > \ell\}, 
$$
and that 
$$
T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
$$
By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
convergence 
$$
\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
$$
where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
$\tilde b(c)$ is a regularly varying norming function which is
_inverse_ to $b(c)$, in the sense that 
$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.

@@

```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset. Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
par(mfrow=c(1,2))
MLestimates(thin_flares_ctre, tail = 0.9, scale = 3 * 1E7)
```

@@

```{r simulated-example, message=FALSE, fig.cap=caption}
k_max <- 500 
thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
par(mfrow=c(1,2))
MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
```

>>>>

#### _Proof of Theorem:_ {-}
We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
and then utilize a result by @MeerschaertStoev08. 
The running maximum process is defined as 
$$
M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
$$
and since we assume that the $J_k$ have a continuous distribution, there exist 
norming functions $a(c)$ and $d(c)$ such that 
$$
\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
\longrightarrow F(\ell^*), \quad t \to \infty
$$
where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
value from the support of $F$. 
The CTRM process is then defined via 
$$
V(t) = M(N(t)), \quad t \ge 0
$$
where $N(t)$ is the renewal process associated with the waiting times 
$W_k$: 
$$
N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
$$
Now a key observation is that
$$
T(\ell) = \inf\{t: V(t) > \ell\}, 
$$
and that 
$$
T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
$$
By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
convergence 
$$
\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
$$
where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
$\tilde b(c)$ is a regularly varying norming function which is
_inverse_ to $b(c)$, in the sense that 
$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.

@@

```{r flares, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset. Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
par(mfrow=c(1,2))
MLestimates(thin_flares_ctre, tail = 0.9, scale = 3 * 1E7)
```

@@

```{r sim, message=FALSE, fig.cap=caption}
k_max <- 500 
thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
par(mfrow=c(1,2))
MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
```
